Understanding the Impact of Socioeconomic and Regional Factors on Health and Educational Outcomes

### 2024-12-08 analysis.qmd

```{r, echo= FALSE, warning = FALSE}
# Since we should not imputate on the outcome, but need to imputate the School.Funding.Adequacy variable, we are feeding the School.Funding.Adequecy variable into a ifelse conditional that will replaced the impuated outcome variable.

@@

mlrmodel <- lm(
  Life.Expectancy ~ Residential.Segregation.Index +
    X..Limited.Access.to.Healthy.Foods +
    X..Uninsured.Adults,
  data = combined)

# Renaming the output names 
renamed <- c(
  "Residential.Segregation.Index" = "Residential Segregation Index (RSI)",
  "X..Limited.Access.to.Healthy.Foods" = "Access to Healthy Foods",
  "X..Uninsured.Adults" = "Pct. of Uninsured Adults")

>>>>

```{r, echo= FALSE, warning = FALSE}
# Since we should not imputate on the outcome, but need to imputate the School.Funding.Adequacy variable, we are feeding the School.Funding.Adequacy variable into a ifelse conditional that will replaced the impuated outcome variable.

@@

mlrmodel <- lm(
  Life.Expectancy ~ Residential.Segregation.Index +
  X..Limited.Access.to.Healthy.Foods +
  X..Uninsured.Adults +
  Region_fac,
  data = combined)

# Renaming the output names 
renamed <- c(
  "Residential.Segregation.Index" = "Residential Segregation Index (RSI)",
  "X..Limited.Access.to.Healthy.Foods" = "Access to Healthy Foods",
  "X..Uninsured.Adults" = "Pct. of Uninsured Adults",
  "Region_facWest" = "Region.W", 
  "Region_facNortheast" = "Region.NE",
  "Region_facMidwest" = "Region.MidW")
